---
title: "Day 2 Homework"
author: "Brock Couch"
date: "2 August 2021"
output:
  html_document:
    theme: spacelab
    toc: no
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Instructions
Answer the following questions and complete the exercises in RMarkdown. Please embed all of your code and push your final work to your repository. Remember, you must remove the `#` for the included code chunks to run. Be sure to add your name to the author header above.  

## Load the libraries
```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(janitor)
library(here)
library(naniar)
``` 

For this homework, we will use data about California colleges. These data are a subset of the national college scorecard (https://collegescorecard.ed.gov/data/). Load the `ca_college_data.csv` as a new object called `colleges`.
```{r}
library(readr)
CA_College<- read_csv("ca_college_data.csv")
```

The variables are a bit hard to decipher, here is a key:  

INSTNM: Institution name  
CITY: California city  
STABBR: Location state  
ZIP: Zip code  
ADM_RATE: Admission rate  
SAT_AVG: SAT average score  
PCIP26: Percentage of degrees awarded in Biological And Biomedical Sciences  
COSTT4_A: Annual cost of attendance  
C150_4_POOLED: 4-year completion rate  
PFTFTUG1_EF: Percentage of undergraduate students who are first-time, full-time degree/certificate-seeking undergraduate students  

1. Use your preferred function(s) to have a look at the data and get an idea of its structure. 
```{r}
str(CA_College)
```

```{r}
summary(CA_College)
```

```{r}
glimpse(CA_College)
```

2. Which cities in California have the highest number of colleges?
```{r}
City_Count<- CA_College%>%
  group_by(CITY)%>%
  summarise(freq=n())
###Los Angeles has the highest number of colleges.
```

3. Based on your answer to #2, make a plot that shows the number of colleges in the top 10 cities.
```{r}
top_n(City_Count,n=10,freq)%>%
  ggplot(aes(x= reorder(CITY, -freq), y=freq))+
  geom_bar(stat = "identity")+
  labs(x="California Cities", y="Number of Colleges")+
  theme(axis.text.x.bottom = element_text(angle = 45, vjust = .6))
```

4. The column `COSTT4_A` is the annual cost of each institution. Which city has the highest average cost?
```{r}
Avg_Cost<-CA_College[!is.na(CA_College$COSTT4_A),]%>%
  group_by(CITY)%>%
  summarise(Avg_Cost=mean(COSTT4_A))%>%
  arrange(desc(Avg_Cost))


City<- CA_College%>%
  group_by(CITY)

###Claremont has the highest average cost.
```

5. Based on your answer to #4, make a plot that compares the cost of the individual colleges in the most expensive city.
```{r}
CA_College%>%
  filter(CITY == "Claremont")%>%
  ggplot(aes(reorder(INSTNM, -COSTT4_A), COSTT4_A))+
  geom_bar(stat = "identity")+
  labs(x="Universities in Claremont, CA",y="Annual Cost")+
  theme(axis.text.x.bottom = element_text(angle = 25, vjust = .75, hjust = .65))
```

6. The column `ADM_RATE` is the admissions rate by college and `C150_4_POOLED` is the four-year completion rate. Use a scatterplot to show the relationship between these two variables. What do you think this means?
```{r}
CA_College%>%
  ggplot(aes(ADM_RATE,C150_4_POOLED))+
  geom_jitter()+
  geom_smooth(method = "lm")
###This means that as acceptance increases, there is a lower proportion of students who graduate.
```

7. Is there a relationship between cost and four-year completion rate? (You don't need to do the stats, just produce a plot). What do you think this means?
```{r}
CA_College%>%
  ggplot(aes(COSTT4_A, C150_4_POOLED))+
  geom_jitter()+
  geom_smooth(method = "lm")

###Yes there is a relationship between cost and four-year completion rate.
```

8. If you wanted to get a degree in biological or biomedical sciences, which campus confers the majority of these degrees? Produce a numerical summary and an appropriate plot.
```{r}
BIO<- CA_College%>%
  select(c(INSTNM, PCIP26))%>%
  arrange(desc(PCIP26))
###University of California-San Diego has the highest proportion of biological or biomedical graduates.

BIO_condensed<- BIO%>%
  subset(PCIP26>0.0) ###Removing zeros and NAs from dataset
BIO_condensed$IDNUM<- seq.int(nrow(BIO_condensed)) ###Giving Institutions unique ids
BIO_condensed$IDNUM<- as.character(BIO_condensed$IDNUM+1000) ###Giving Institutions unique ids

BIO_condensed[1:10,]%>%
  ggplot(aes(IDNUM, PCIP26))+
  geom_bar(stat = "identity")+
  labs(x="Unique ID of University",y="Percentage of Degrees Awarded in Biological and Biomedical Sciences")+
  theme(axis.title.y = element_text(size=10, hjust = 1, margin=margin(r=10)), 
        axis.title.x = element_text(margin = margin(t=10)))

```


## Knit Your Output and Post to your Github